Trajipaq_sentiment_cr

### 2023-06-20 1. Trajipaq_sentiment/2. Codes/Trajipaq_sentiment_an.Rmd
update WGI

```{r}
reg_4 <- glm(formula = vae_arrival ~ VD1, data = trajipaq)

summary(reg_4)

cor.test(trajipaq$vae_arrival, trajipaq$VD1)

>>>>

```{r}
reg_4 <- glm(formula = vae_arrival ~ VD1 + VD2 + VD4 + VD5, data = trajipaq) # voice and acountability
reg_5 <- glm(formula = pve_arrival ~ VD1 + VD2 + VD4 + VD5, data = trajipaq) # Political stability No Violence
reg_6 <- glm(formula = gee_arrival ~ VD1 + VD2 + VD4 + VD5, data = trajipaq) # Government Effectiveness
reg_7 <- glm(formula = rqe_arrival ~ VD1 + VD2 + VD4 + VD5, data = trajipaq) # Regulatory quality
reg_8 <- glm(formula = rle_arrival ~ VD1 + VD2 + VD4 + VD5, data = trajipaq) # Rule fo law
reg_9 <- glm(formula = cce_arrival ~ VD1 + VD2 + VD4 + VD5, data = trajipaq) # Control of corruption

summary(reg_4)
summary(reg_5)
summary(reg_6)
summary(reg_7)
summary(reg_8)
summary(reg_9)

cor.test(trajipaq$vae_arrival, trajipaq$VD2)

### 2023-06-20 1. Trajipaq_sentiment/2. Codes/Trajipaq_sentiment_cr.Rmd
update WGI

wgidataset_2021 <- filter(wgidataset, year == 2021)

trajipaq <- trajipaq %>%
  left_join(wgidataset_2021, by = c("Q11" = "countryname"))

>>>>

wgidataset_2021 <- filter(wgidataset, year == 2021)
wgidataset_canada <- filter(wgidataset, countryname == "Canada")

trajipaq <- trajipaq %>%
  left_join(wgidataset_2021, by = c("Q11" = "countryname"))%>%
  left_join(wgidataset_canada, by = c("annee_qc" = "year"))

trajipaq <- trajipaq %>%
